---
title: "R Notebook"
output: html_notebook
---

# Task 2: Cake ingredients

## Analysis file

In this file I am going to analyse some characteristics of the data. I will start answering to the following questions:


 1.Which cake has the most cocoa in it?
 2.For sponge cake, how many cups of ingredients are used in total?
 3.How many ingredients are measured in teaspoons?
 4.Which cake has the most unique ingredients?
 5.Which ingredients are used only once?
 
 
First of all I will read the cleaned dataset I created in the .R script.

```{r}
library(tidyverse)
```

```{r}
cakes <- read_csv(here::here("clean_data/cakes.csv"))
```

###  1.Which cake has the most cocoa in it?

```{r}
cakes %>% 
  filter(ingredient == "Cocoa") %>% 
  arrange(desc(dose))
```

The cake with most Cocoa is the 'One Bowl Chocolate'.

###  2.For sponge cake, how many cups of ingredients are used in total?


```{r}
cakes %>% 
  filter(cake == "Sponge" & measure == "cup") %>% 
  summarise(total_ingr_cups_sponge = sum(dose))
```

###  3.How many ingredients are measured in teaspoons?


```{r}
cakes %>% 
  filter(measure == "teaspoon") %>% 
  distinct(ingredient) %>% 
  summarise(num_ingredients_teaspoon_mis = n())
```




```{r}

```





